Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-03-06 paper_comparison/paper_comparison/paper_comparison.Rmd
Fix cross reference issue

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Three replications are made for $3 \times 4 = 12$ combinations of common factors $n$ and fitted value distribution, results in $12 \times 3 = 36$ lineups included in data collection period III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated directly from the null model. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under $H_0$.

@@

The data of the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{sampling-from-the-null-distribution}.

>>>>

As mentioned in Section \ref{power-of-the-tests}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Three replications are made for $3 \times 4 = 12$ combinations of common factors $n$ and fitted value distribution, results in $12 \times 3 = 36$ lineups included in data collection period III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{visual-test-procedure-based-on-lineups}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated directly from the null model. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under $H_0$.

@@

The data of the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{visual-test-procedure-based-on-lineups}.

### 2023-03-06 paper_comparison/paper_comparison/paper_comparison.tex
Fix cross reference issue

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using null lineups. Three replications are made for
\(3 \times 4 = 12\) combinations of common factors \(n\) and fitted
value distribution, results in \(12 \times 3 = 36\) lineups included in
data collection period III. In these lineups, the data of the data plot
is generated from a model with zero effect size, while the data of the
19 null plots are generated using the same simulation method discussed
in Section \ref{sampling-from-the-null-distribution}. This generation
procedure differs from the canonical Rorschach lineup procedure, which
requires that all 20 plots are generated directly from the null model.
However, these lineups serve the same fundamental purpose: to assess the
number of visually interesting plots generated under \(H_0\).

>>>>

As mentioned in Section \ref{power-of-the-tests}, \(\alpha\) used in
Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null
lineups. Three replications are made for \(3 \times 4 = 12\)
combinations of common factors \(n\) and fitted value distribution,
results in \(12 \times 3 = 36\) lineups included in data collection
period III. In these lineups, the data of the data plot is generated
from a model with zero effect size, while the data of the 19 null plots
are generated using the same simulation method discussed in Section
\ref{visual-test-procedure-based-on-lineups}. This generation procedure
differs from the canonical Rorschach lineup procedure, which requires
that all 20 plots are generated directly from the null model. However,
these lineups serve the same fundamental purpose: to assess the number
of visually interesting plots generated under \(H_0\).
